Instructions for developing new pages for the MarineOmics webpage

### 2023-02-22 submissions_instructions.Rmd
publishing submissions_instructions page to website and pushing some other cache files
testing whether we can keep each page's files in one folder to organize the repo

```{r #setup, echo = FALSE, message = FALSE}
library(knitr)
knitr::opts_chunk$set(
	fig.height = 5,
	fig.width = 10,
	cache = FALSE
)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc")
```

@@

If you are interested in submitting new content to the
MarineOmics.github.io website, this is the guide for you! While the
website managers will work with you to help prepare and publish your new
page, this guide can be a useful resource as you develop your content.
Below we provide general instructions as well as examples of how to
build specific features (eg., tables, code chunks). Prior to publishing
new pages, please contact the current Website Manager Jason Johns
(jasonjohns[at]ucsb.edu). Do not hesitate to reach out with any other
questions, comments, or features you'd like added to this guide.

@@

    knitr::include_graphics("images/Rivera_etal_fig.png")

>>>>

```{r #setup, echo = FALSE, message = FALSE}
library(knitr)
knitr::opts_chunk$set(
	fig.height = 5,
	fig.width = 10,
	cache = TRUE
)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = TRUE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc")
```

@@

If you are interested in submitting new content to the
MarineOmics.github.io website, this is the guide for you! While the
website managers will work with you to help prepare and publish your new
page, this guide can be a useful resource as you develop your content.
Below we provide general instructions as well as examples of how to
build specific features (eg., tables, code chunks). Prior to developing
new pages, please contact the current Website Manager Jason Johns
(jasonjohns[at]ucsb.edu). Do not hesitate to reach out with any other
questions, comments, or features you'd like added to this guide.

@@

    knitr::include_graphics("submissions_instructions/Rivera_etal_fig.png")
